---
name: Samuel    
surname: Thompson
position: "PhD researcher"
address: "School of Biological Sciences, University of Western Australia"
email: "samt9892@hotmail.com"
github: samt9892
linkedin: samt9892
researchgate: Samuel-Thompson-17
website: 
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

# About me

I use novel sampling methods, computers and large data sets to answer biological questions, typically in marine vertebrates. My research has focused on the development and deployment of a novel sampler capable of simultaneously collecting environmental DNA (eDNA), stereo-video imagery and oceanographic data, along with the development of a new family-specific eDNA metabarcoding primer set targeting Lutjanidae (Snapper). I investigate the spatial distribution of marine vertebrate species in the context of anthropogenic change; especially the presence of restricted-access marine areas such as Marine Parks and offshore infrastructure.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~loc, ~ details,
  "PhD", "2020-present", "University of Western Australia", "Perth, Australia", list('eDNA metabarcoding PhD with the Marine Ecology Fisheries Research Group and the Jarman lab', 'Developed a sampling system capable of collecting 360-degree stereo-video, water samples and oceanographic data at depths up to 600m', 'Designed a family-specific metabarcoding primer set for Lutjanidae (snapper)', 'Worked extensively with industry (BHP)'), 
  "Master of  Oceanography", "2017-2018", "University of Southampton", "Southampton, United Kingdom", list('Studied all forms of oceanography with a focus on biological oceanography and deep-sea ecology', 'In my research project I worked on characterising deep-sea megafauna of the Kiribati region using a towed camera system (published in Frontiers in Marine Science 2019)'),
  "Bachelor of Biochemistry (with honours)", "2010-2014", "University of Kent", "Kent, United Kingdom", list('Studied general life sciences with a focus on microbiology/genetics', 'In my final project I worked on genome duplication events in the marine chordate Amphioxus'),
) %>% 
  detailed_entries(Degree, Year, Institution, loc, details)
```

# Employment

```{r}
tribble(
  ~Year, ~Role, ~Location, ~Institution, ~Details,
  "2021-present", "Research assistant (part-time)", "Perth", "Minderoo", list("Research assistant with the Minderoo OceanOmics team during offshore expeditions", "Working onboard the Pangaea Ocean Explorer, conducting eDNA sampling, extraction, amplification, purification and sequencing", "Has provided me with a unique opportunity to conduct end-to-end sampling to sequencing on an offshore vessel"),
  "2021-present", "Laboratory demonstrator (part-time)", "Perth", "University of Western Australia", list("BIOL1131: Plant and Animal Biology", "Laboratory demonstrator and tutor for both face-to-face and online delivery formats", "Marker for marine component", "Guest Lecturer: Amphioxus: A model for developmental biology"),
  "2019-2019", "Oceanographer", "Perth", "RPS MetOcean", list("Working in the data resources department", "Work processing, QCing and interpreting  large oceanographic datasets through a linux environment and the command line", "Data from instruments including: ADCPs, CTDs, LIDAR buoys, Wave rider buoys"),
  "2019-2020", "Windsurfing and sailing instructor (part-time)", "Perth", "Royal Perth Yacht Club", list("Working as a dual qualified windsurfing and sailing instructor at a prestigious Perth yacht club", "Delivering both practical and theoretical lessons to groups of all ages and abilities ranging from age 8 up to 70"),
  "2015-2017", "Analytical chemist", "Kent, United Kingdom", "Mylan", "Key R&D team member during the ANDA submission to the FDA for a generic Advair drug product.
  Conducted inhalation-specific lab techniques including aerodynamic particle size distribution, dissolution and emitted dose testing.
  Use, calibration, maintenance and troubleshooting of analytical chemistry instrumentation including HPLC and Raman spectrometers.
  Worked abroad in Dublin training new staff and setting up equipment in a new, purpose built QC lab for Mylan's European inhalation manufacturing facility"
) %>% 
  detailed_entries(Role, Year, Institution, Location, Details)
```


# Other Skills

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~loc, ~ details,
  "Bash, R, HTML, Python", "", "Coding languages", "", list( "Shell scripting; building and running pipelines for processing large bioinformatic and oceanographic datasets via command-line", "Highly proficient with the configuration and operation of both native and virtual Linux environments (WSL2)", "Familiar with wide variety of R packages, especially for ecological statistics and spatial analysis", "Highly familiar with version control systems: Git and Docker", "Have my own hardcoded website written in HTML and styled using CSS"),
  "Electrical, Mechanical, Woodwork, Ropework, Boatwork", "", "Practical Skills", "", list("Highly proficient at building and troubleshooting 12v automotive and marine systems", "Highly proficient at troubleshooting software/hardware related PC issues; I have built multiple desktop PCs and completed many initial OS installs and setups using various windows and linux distributions",  "Intermediate mechanical knowledge; especially 4x4 and diesel automotive systems", "Basic carpentry and joinery skills from building multiple campervans", "Basic ropework / winch skills", "I have participated >1000 deployments of various marine sampling equipment on a variety of vessel types from the Southampton Solent to the Southern Ocean")
) %>% 
  detailed_entries(Degree, Year, Institution, loc, details)
```

# Licenses & certifications

```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,
  "2022-2023", "Advanced resuscitation", "PADI", "Oxygen provider and CPR",
  "2021-2024", "First Aid", "PADI", "",
  "2020", "4WD training", "Drive Safe WA", "RIIVEH201D: Operate light vehicle, TLIC1051: Operate Commerical Vehicle, TLIC2025: Operate four wheel drive vehicle, TLIF2010: Apply fatigue management strategies, RIIVEH305E: Drive and recover a four wheel drive vehicle, PMASUP236: Operate vehicles in the field",
  "2020", "Recreational skippers ticket", "DOT", "",
  "2017", "Advanced Open Water Diver", "PADI", "",
  "2014", "Dinghy sailing instructor", "RYA", "",
  "2013", "Safety boat", "RYA", "",
  "2012", "Powerboat level 2", "RYA", "",
  "2012", "Start windsurfing instructor", "RYA", ""
    
  
) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```

# Scientific voyages
```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,
  "2022 (22 days)", "Fremantle > Cocos Keeling Islands", "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2022 (12 days)", "Carnarvon > Ningaloo Marine Park", "Keshi Mer", "Voyage lead - UWA Marine Ecology Group. Surveying paleocoastline features with stereo-BRUVs, novel samplers, CTD and eDNA",
  "2022 (10 days)", "Fremantle > Abrolhos Islands > Fremantle", "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2022 (14 days", "Esperance > Israelite bay > Fremantle", "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2021 (10 days)", "Coral Bay > Exmouth Gulf" , "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2021 (28 days)", "Dongara > Onslow, WA", "Adrianus", "PhD Student - UWA Marine Ecology group surveying Marine Parks, proposed park zones and offshore oil and gas infrastructure using stereo-BRUVs, novel samplers, CTD and eDNA",
) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```
# Presentations

```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,
  "2023", "Simultaneous eDNA and visual surveying of the marine environment", "Australia and New Zealand eDNA conference", "ECR presenter",
  "2021", "Amphioxus: A model for developmental biology", "UWA - BIOL1131: Plant and Animal Biology", "Guest Lecturer",
  "2021", "Research update", "UWA - School of biological sciences postgraduate retreat", "Student presenter",
  "2020", "Research proposal", "UWA- School of Biological sciences Friday seminar series", "PhD research proposal"

) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```

# Awards and Funding

```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,

  "2020-2024", "Grant: Biodiversity and societal benefits of restricted access marine areas", "BHP/UWA", "With Prof. Julian Partridge, Prof. Simon Jarman, Prof. Gary Kendrick, Dr. Tim Langlois, Dr Matt Navarro. Total funding: AUSD 666,524.",
  "2023", "Award: CSIRO Early-career researcher conference bursary", "CSIRO", "Grant to attend the 2023 Australia and New Zealand eDNA conference in Hobart. Total funding: AUSD 600"
) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```

# Publications

```{r}
scholar::get_publications("sv3D4R8AAAAJ") %>% 
    dplyr::filter(!is.na(year)) %>%  # filter out weird trash
    arrange(desc(year)) %>% # newest papers first
    detailed_entries(
        with=title,
        when=year,
        what=author,
        where=journal
        )
```
