---
name: Samuel    
surname: Thompson
position: "PhD researcher"
address: "School of Biological Sciences, University of Western Australia"
email: "samt9892@hotmail.com"
github: samt9892
linkedin: samt9892
researchgate: Samuel-Thompson-17
website: 
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

# About me

I use novel sampling methods, computers and large data sets to answer biological questions, especially in marine vertebrates. My research has focused on the development and deployment of a novel sampler capable of collecting  environmental DNA (eDNA), stereo-video imagery and oceanographic data, along with a new family-specific eDNA metabarcoding primer set targeting Lutjanidae (snapper). I investigate the spatial distribution of marine vertebrate species in the context of anthropogenic change; especially the presence of restricted-access marine areas.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~loc, ~ details,
  "PhD", "2020-present", "University of Western Australia", "Perth, Australia", list('eDNA metabarcoding PhD with the Marine Ecology Fisheries Research Group and the Jarman lab', 'Developed a sampling system capable of collecting 360-degree stereo-video, water samples and oceanographic data at depths up to 600m', 'Designed a family-specific metabarcoding primer set for Lutjanidae (snapper)', 'Worked extensively with industry (BHP)'), 
  "Master of Biological Oceanography", "2017-2018", "University of Southampton", "Southampton, United Kingdom", list('Studied all forms of oceanography with a focus on biological oceanography and deep-sea ecology', 'In my final project I worked on characterising the abyssal megafauna of the Kiribati region from ROV imagery (published in Frontiers in marine science 2019)'),
  "Bachelor of Biochemistry (with honours)", "2008-2012", "University of Kent", "Kent, United Kingdom", list('Studied general life sciences with a focus on microbiology/genetics', 'In my final project I worked on genome duplication events in the marine chordate Amphioxus'),
) %>% 
  detailed_entries(Degree, Year, Institution, loc, details)
```

# Employment

```{r}
tribble(
  ~Year, ~Role, ~Location, ~Institution, ~Details,
  "2021-present", "Research assistant (part-time)", "Perth", "Minderoo", list("Research assistant with the Minderoo OceanOmics team during offshore expeditions", "Working onboard the Pangea Ocean Explorer, conducting eDNA sampling, extraction, amplification, purification and sequencing", "Has provided me with a unique opportunity to conduct end-to-end sampling to sequencing on an offshore vessel"),
  "2021-present", "Laboratory demonstrator (part-time)", "Perth", "University of Western Australia", list("BIOL1131: Plant and Animal Biology", "Laboratory demonstrator and tutor for both face-to-face and online delivery formats", "Marker for marine component", "Guest Lecturer: Amphioxus: A model for developmental biology"),
  "2019-2019", "Oceanographer", "Perth", "RPS MetOcean", list("Working in the data resources department", "Work processing, QCing and interpretating  large oceanographic datasets through a linux environment and the command line", "Data from instruments including: ADCPs, CTDs, LIDAR buoys, Wave rider buoys"),
  "2019-2020", "Windsurfing and sailing instructor (part-time)", "Perth", "Royal Perth Yacht Club", list("Working as a dual qualified windsurfing and sailing instructor at a revered Perth yacht club", "Delivering both practical and theoretical lessons to groups of all ages and abilities including as young as 8 years old and as old as 70"),
  "2015-2017", "Analytical chemist", "Kent, United Kingdom", "Mylan", "Key R&D team member during the ANDA submission to the FDA for a generic Advair drug product.
  Conducted inhalation-specific lab techniques including aerodynamic particle size distribution, dissolution and emitted dose testing.
  Use, calibration, maintainance and troubleshooting of analytical chemistry instrumentation including HPLC and Raman spectrometers.
  Worked abroad in Dublin training new staff and setting up equipment in a new, purpose built QC lab for Mylan's European inhalation manufacturing facility"
) %>% 
  detailed_entries(Role, Year, Institution, Location, Details)
```


# Other Skills

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~loc, ~ details,
  "Bash, R, HTML, Python", "", "Coding languages", "", list( "Shell scripting; building and running pipelines for processing large bioinformatic and oceanographic datasets via command-line", "Highly proficent with the configuration and operation of both native and virtual Linux environments (WSL2)", "Familiar with wide variety of R packages, especially for ecological statistics and spatial analysis", "Highly familiar with version control systems: Git and Docker", "Have my own hardcoded website written in HTML and styled using CSS"),
  "Electrical, Mechanical, Woodwork, Ropework, Boatwork", "", "Practical Skills", "", list("Highly proficent with building and troubleshooting 12v automotive and marine systems", "Highly proficent at troubleshooting software/hardware related PC issues; I have built multiple desktop PCs and completed many initial OS installs and setups using various windows and linux distributions",  "Intermediate mechanical knowledge; especially 4x4 and diesel automotive systems", "Basic carpentry and joinery skills from building multiple campervans", "Basic ropework / winch skills", "I have participated >1000 deployments of various marine sampling equipment on a variety of vessel types from the Southampton Solent to the Southern Ocean")
) %>% 
  detailed_entries(Degree, Year, Institution, loc, details)
```

# Licenses & certifications

```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,
  "2022-2023", "Advanced resusitation", "PADI", "Oxygen provider and CPR",
  "2021-2024", "First Aid", "PADI", "",
  "2020", "4WD training", "Drive Safe WA", "RIIVEH201D: Operate light vehicle, TLIC1051: Operate Commerical Vehicle, TLIC2025: Operate four wheel drive vehicle, TLIF2010: Apply fatigue management strategies, RIIVEH305E: Drive and recover a four wheel drive vehicle, PMASUP236: Operate vehicles in the field",
  "2020", "Recreational skippers ticket", "DOT", "",
  "2017", "Advanced Open Water Diver", "PADI", "",
  "2014", "Dinghy sailing instructor", "RYA", "",
  "2013", "Safety boat", "RYA", "",
  "2012", "Powerboat level 2", "RYA", "",
  "2012", "Start windsurfing instructor", "RYA", ""
    
  
) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```

# Presentations

```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,
  "2021", "Amphioxus: A model for developmental biology", "UWA - BIOL1131: Plant and Animal Biology", "Guest Lecturer",
  "2021", "Research update", "UWA - School of biological sciences postgradiate retreat", "Student presenter",
  "2020", "Research proposal", "UWA- School of Biological sciences friday seminar series", "PhD research proposal"

) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```

# Awards and Funding

```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,

  "2020-2024", "Grant: Biodiversity and societal benefits of restricted access marine areas", "BHP/UWA", "With Prof. Julian Partridge, Prof. Simon Jarman, Prof. Gary Kendrick, Dr. Tim Langlois, Dr Matt Navarro. Total funding: AUSD 666,524.",
) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```

# Publications

```{r}
scholar::get_publications("sv3D4R8AAAAJ") %>% 
    dplyr::filter(!is.na(year)) %>%  # filter out weird trash
    arrange(desc(year)) %>% # newest papers first
    detailed_entries(
        with=title,
        when=year,
        what=author,
        where=journal
        )
```
