---
name: Samuel    
surname: Thompson
position: "Data Scientist / Research Associate"
address: "School of Molecular and Life Sciences, Curtin University"
email: "samt9892@hotmail.com"
github: samt9892
linkedin: samt9892
researchgate: Samuel-Thompson-17
website: 
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)

# Add custom LaTeX commands for better spacing
options(knitr.table.format = "latex")
```

# About me

I use novel sampling methods, computers and large genetic datasets to answer biological questions, typically in marine vertebrates. My research has focused on the development and deployment of a novel sampler capable of simultaneously collecting environmental DNA (eDNA), stereo-video imagery and oceanographic data, investigating  the spatial distribution of marine vertebrate species in the context of anthropogenic change; especially the presence of restricted-access marine areas such as Marine Parks and offshore infrastructure. I am particularly passionate about the development of novel software tools to standardise and automate the analysis, reporting and display of ecological data, particularly eDNA metabarcoding data. 

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~loc, ~ details,
  "PhD", "2020-2024", "University of Western Australia", "Perth, Australia", list('Environmental DNA (eDNA) metabarcoding PhD with the Marine Ecology Fisheries Research Group and the Jarman lab', 'Developed a sampling system capable of collecting 360-degree stereo-video, water samples and oceanographic data at depths up to 600m', 'Designed a family-specific eDNA metabarcoding primer set for Lutjanidae (snapper)', 'Developed multiple bioinformatic pipelines and data science tools for processing genetic, visual and oceanographic datasets', 'Worked extensively with industry (BHP) and fishing industry', '\\vspace{0.2cm}'), 
  "Master of  Oceanography", "2017-2018", "University of Southampton", "Southampton, United Kingdom", list('Studied all forms of oceanography with a focus on biological oceanography and deep-sea ecology', 'Research project focussed on characterising deep-sea megafauna of the Kiribati region with towed-camera systems (published in Frontiers in Marine Science 2019)', '\\vspace{0.2cm}'),
  "Bachelor of Biochemistry (First Class with honours)", "2010-2014", "University of Kent", "Kent, United Kingdom", list('Studied general life sciences with a focus on genetics and molecular biology', 'Research project focussed on using novel bioinformatic tools to understanding genome duplication events in chordate species','\\vspace{0.2cm}'),
) %>% 
  detailed_entries(Degree, Year, Institution, loc, details)
```

# Employment

```{r}
tribble(
  ~Year, ~Role, ~Location, ~Institution, ~Details,
  "2023-present", "Data Scientist / Research Associate", "Perth", "Curtin University", list("Data scientist / Bioinformatician for eDNA Frontiers, TrEnD Laboratory and eDGES Program at Curtin University", "Single-handedly building a full software stack (PostgreSQL, AWS, R/Python) to automate the analysis, curation, storage and display of large eDNA datasets", "Contributing data science expertise to the Fish Ecology Laboratory at Curtin University", "Communications manager for the eDNA for Global Environment Studies (eDGES) project at Curtin University")
) %>% 
  detailed_entries(Role, Year, Institution, Location, Details)
```
\vspace{0.2cm}
```{r}
tribble(
  ~Year, ~Role, ~Location, ~Institution, ~Details,
  "2021-2024", "Research assistant (part-time)", "Perth", "Minderoo Foundation", list("Research assistant with the Minderoo OceanOmics team during offshore expeditions", "Working onboard the Pangaea Ocean Explorer, conducting environmental and genomic DNA sampling, extraction, amplification, purification, sequencing and data analysis", "Opportunity to undertake knowledge transfer of eDNA techniques to traditional ranger groups", "Has provided me with a unique opportunity to conduct end-to-end sampling to sequencing on an offshore vessel", "Conducting onboard bioinformatics analysis using a high-performance computing system")
) %>% 
  detailed_entries(Role, Year, Institution, Location, Details)
```
\vspace{0.2cm}
```{r}
tribble(
  ~Year, ~Role, ~Location, ~Institution, ~Details,
  "2021-2022", "Laboratory demonstrator (part-time)", "Perth", "University of Western Australia", list("BIOL1131: Plant and Animal Biology", "Laboratory demonstrator and tutor for both face-to-face and online delivery formats", "Marker for marine and genetics components", "Guest Lecturer: Amphioxus: A model for developmental biology")
) %>% 
  detailed_entries(Role, Year, Institution, Location, Details)
```
\vspace{0.2cm}
```{r}
tribble(
  ~Year, ~Role, ~Location, ~Institution, ~Details,
  "2019-2019", "Data Scientist / Oceanographer", "Perth", "RPS MetOcean", list("Working in the data sciences department", "Work processing, QCing and interpreting  large oceanographic datasets through a linux environment, custom software and shell scripts", "Data from instruments including: ADCPs, CTDs, LIDAR buoys, Wave rider buoys")
) %>% 
  detailed_entries(Role, Year, Institution, Location, Details)
```
\vspace{0.2cm}
```{r}
tribble(
  ~Year, ~Role, ~Location, ~Institution, ~Details,
  "2019-2020", "Windsurfing and sailing instructor (part-time)", "Perth", "Royal Perth Yacht Club", list("Working as a dual qualified windsurfing and sailing instructor at a prestigious Perth yacht club", "Delivering both practical and theoretical lessons to groups of all ages and abilities ranging from age 8 up to 70")
) %>% 
  detailed_entries(Role, Year, Institution, Location, Details)
```
\vspace{0.2cm}
```{r}
tribble(
  ~Year, ~Role, ~Location, ~Institution, ~Details,
  "2015-2017", "Analytical chemist", "Kent, United Kingdom", "Mylan", list("Key research team member during the ANDA submission to the FDA for a generic Advair drug product", "Conducted inhalation-specific lab techniques including aerodynamic particle size distribution, dissolution and emitted dose testing", "Use, calibration, maintenance and troubleshooting of analytical chemistry instrumentation including HPLCs and Raman spectrometers.", "Worked abroad in Dublin training new staff and setting up equipment in a new, purpose built QC lab")
) %>% 
  detailed_entries(Role, Year, Institution, Location, Details)
```

# Skills

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~loc, ~ details,
  "R, SQL, Python, HTML, CSS, Java, Bash", "", "Coding languages", "", list( "Shell scripting; building and running pipelines for processing large bioinformatic and oceanographic datasets via command-line", "Highly proficient in full-stack development, AWS (EC2, S3, RDS) infrastructure, mySQL / postgreSQL databases and R/Python shiny frontend", "Highly familiar with wide variety of R and Python packages, particularly for bioinformatics, ecological statistics and spatial analyses", "Highly familiar with  spatial analyses in arcGIS or qGIS", "Highly familiar with multivariate statistical analyses in both R or Primer", "Highly familiar with version control and containerisation systems: Git, Docker and Singularity", "Familiar with HTML and CSS for the design and styling of reports and websites"),
) %>% 
  detailed_entries(Degree, Year, Institution, loc, details)
```
\vspace{0.2cm}
```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~loc, ~ details,
  "Electrical, Mechanical, Woodwork, Ropework, Boatwork", "", "Practical Skills", "", list("Highly proficient at building and troubleshooting 12v automotive and marine systems", "Highly proficient at troubleshooting software/hardware related PC issues; I have built multiple desktop PCs and completed many initial OS installs and setups using various windows and linux distributions",  "Intermediate mechanical knowledge; especially 4x4 and diesel automotive systems", "Basic ropework / winch operation skills", "I have participated >1000 deployments of  marine sampling equipment on a variety of vessels from the Southampton Solent to the Southern Ocean"),
) %>% 
  detailed_entries(Degree, Year, Institution, loc, details)
```
# Licences & certifications

```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,
  "2023-2024", "First Aid + Advanced resuscitation", "PADI", "Oxygen provider and CPR",
  "2020", "4WD training", "Drive Safe WA", "RIIVEH201D: Operate light vehicle, TLIC1051: Operate Commerical Vehicle, TLIC2025: Operate four wheel drive vehicle, TLIF2010: Apply fatigue management strategies, RIIVEH305E: Drive and recover a four wheel drive vehicle, PMASUP236: Operate vehicles in the field",
  "2020", "Recreational skippers ticket", "DOT", "",
  "2017", "Advanced Open Water Diver", "PADI", "",
  "2014", "Dinghy sailing instructor", "RYA", "",
  "2013", "Safety boat", "RYA", "",
  "2012", "Powerboat level 2", "RYA", "",
  "2012", "Start windsurfing instructor", "RYA", ""
) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```

# Scientific voyages
```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,
  "2024 (26 days)", "Sydney -> Brisbane", "RV Investigator", "Research Assistant - Minderoo OceanOmics / CSIRO",
  "2024 (14 days)", "Perth -> Abrohlos", "RV naturaliste", "Research Assistant - Minderoo OceanOmics / UWA Deep-Sea Research Centre", 
  "2023 (8 days)", "Perth -> Ningaloo Plateau", "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2023 (30 days)", "Christmas Island -> Cocos Keeling Islands -> Fremantle", "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics / UWA Deep-Sea Research Group",
  "2023 (10 days)", "Fremantle -> Abrolhos Islands -> Fremantle", "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2023 (10 days)", "Esperance -> Albany", "Immortalis", "Research Assistant - Minderoo OceanOmics",
  "2022 (22 days)", "Fremantle -> Cocos Keeling Islands", "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2022 (12 days)", "Carnarvon -> Ningaloo Marine Park", "Keshi Mer", "Research lead - UWA Marine Ecology Group. Surveying paleocoastline features with stereo-BRUVs, novel samplers, CTDs and environmental DNA",
  "2022 (10 days)", "Fremantle -> Abrolhos Islands -> Fremantle", "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2022 (14 days)", "Esperance -> Israelite bay -> Fremantle", "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2021 (10 days)", "Coral Bay -> Exmouth Gulf" , "Pangaea Ocean Explorer", "Research Assistant - Minderoo OceanOmics",
  "2021 (28 days)", "Dongara -> Onslow, WA", "Adrianus", "PhD Student - UWA Marine Ecology group. Surveying Marine Parks, proposed park zones and offshore oil and gas infrastructure using stereo-BRUVs, novel samplers, CTDs and environmental DNA",
) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```
# Presentations and Guest Lectures

```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,
  "2024-present", "Curtin University BioBlitz: Community metabarcoding", "Curtin University, Bentley and Singapore campuses", "Technical Lead",
  "2023", "Simultaneous eDNA and visual surveying of the marine environment", "Australia and New Zealand eDNA conference", "ECR presenter",
  "2021", "Amphioxus: A model for developmental biology", "UWA - BIOL1131: Plant and Animal Biology", "Guest Lecturer",
  "2021", "Research update", "UWA: School of Biological Sciences", "Student presenter",
  "2020", "Research proposal", "UWA: School of Biological Sciences", "PhD research proposal"

) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```
\newpage
# Awards and Funding

```{r}
tribble(
  ~Year, ~Role, ~Organisation, ~Details,
  "2020-2024", "Grant: Biodiversity and societal benefits of restricted access marine areas", "BHP/UWA", "With Prof. Julian Partridge, Prof. Simon Jarman, Prof. Gary Kendrick, Dr. Tim Langlois, Dr Matt Navarro. Total funding: AUSD $666,524.",
  "2023", "Award: CSIRO Early-career researcher conference bursary", "CSIRO", "Grant to attend the 2023 Australia and New Zealand eDNA conference in Hobart. Total funding: AUSD $600"
) %>% 
  detailed_entries(when=Year, with=Role, where=Organisation, what=Details)
```

# Publications

```{r}
scholar::get_publications("sv3D4R8AAAAJ") %>% 
    dplyr::filter(!is.na(year)) %>%  # filter out weird trash
    arrange(desc(year)) %>% # newest papers first
    detailed_entries(
        with=title,
        when=year,
        what=author,
        where=journal
        )
```
